surfing

### 2021-05-08 inst/surfing.Rmd
rewording

@fischer1969

[@fischer1969]

[-@fischer1969]

@@

Surfing is a popular and growing activity in terms of both
participation and viewing.  Competitive surfing involves surfers
competing against one or two other surfers in heats lasting 30-50
minutes.  Points are awarded on a 10-point scale: each of five judges
awards points to a surfer riding a particular wave.  The World Surf
League (WSL) is the main governing body of surfing competitions.  The
WSL conducts a world tour in which the best ranked 34 surfers compete;
in addition, at each tour venue, two "wildcard" surfers also enter the
competition, who are ignored here.  The 2019 WSL tour saw competitive
events held at eleven different surf locations.

The typical format is as follows.  Up to four surfers---the
competitors---are in the water simultaneously, watched by up to five
judges.  Subject to surfing etiquette, competitors are free to catch a
wave at their discretion within the heat's time window, typically
20-30 minutes.  The judges rate each wave ride and award points to the
surfer based on a range of subjective criteria including commitment
and degree of difficulty, innovation and variety of manoeuvres, and
transition between manoeuvres.  The top score and bottom score among
the five judges are removed and the remaining three judges' scores are
averaged to give the final score for the surfer for that wave.  Each
surfer's aggregate score is given by the average of the two
highest-scoring waves.  The winner of the tournament is the surfer
with the highest aggregate score.

@@

>>>>

@@

Surfing is a popular and growing activity in terms of both
participation and viewing [@warshaw2010].  Competitive surfing
involves surfers competing against one or two other surfers in heats
lasting 30-50 minutes [@booth1995].  Points are awarded on a 10-point
scale: each of five judges awards points to a surfer riding a
particular wave.  The World Surf League (WSL) is the main governing
body of surfing competitions [@wsl].  The WSL conducts a world tour in
which the best ranked 34 surfers compete; in addition, at each tour
venue, two "wildcard" surfers also enter the competition, who are
ignored here.  The 2019 WSL tour saw competitive events held at eleven
different surf locations.

The typical format is as follows.  Up to four surfers---the
competitors---are in the water simultaneously, watched by up to five
judges.  Subject to surfing etiquette, competitors are free to catch a
wave at their discretion within the heat's time window, typically
20-30 minutes.  The judges rate each wave ride and award points to the
surfer based on a range of subjective criteria such as stylish
execution and transition of manoeuvres, but also credit elements such
as the difficulty and novelty of the performance.  The top score and
bottom score among the five judges are removed and the remaining three
judges' scores are averaged to give the final score for the surfer for
that wave.  Each surfer's aggregate score is given by the average of
the two highest-scoring waves.  The winner is the surfer with the
highest aggregate score.

@@

# references
